\huge Fast Evaluation of Intermolecular Charge Transfer Energy: New Approach Based on One-Electron Effective Potentials

### 2019-06-28 papers/conference/1.MQM_2019/poster-84x118cm.tex
Revision of Poster

\begin{textblock*}{440mm}(10mm,135mm)
\begin{block}{Ab Initio Charge Transfer Energy in Fragment-Based Modelling}
 \begin{itemize}
   \item CT energy is an {\color{green} important} stabilizing contribution to the total interaction energy [1]
   \item It is {\color{red} very costly} to compute and generally not directly included in most force fields
   \item {\color{green} EFP2 model} implements efficient CT energy estomator [2,3]
   \item However, EFP2 CT energy is {\color{red} 30-40 times slower} then evaluating other components [3]
   \item In effect, this CT term is usually {\color{red} not included} in condensed matter modelling [4]
 \end{itemize}
\end{block}
\end{textblock*}

\begin{textblock*}{250mm}(10mm,253mm)
\begin{block}{Our Approach}
 \begin{itemize}
   \item Consider Murrell et al.'s perturbation theory [5]
   \item Apply OEP method to eliminate ERI's
   \item Adapt the CT term to the EFP2 method [2,3]
 \end{itemize}
\end{block}
\end{textblock*}

\begin{textblock*}{180mm}(270mm,253mm)
\begin{block}{CT energy by Murrell et al. [5]}
  \vskip-2ex
  \begin{equation*}
    \Delta E_{\rm CT}^{A\rightarrow B} = 2\sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir}
     \frac{\vert V_{in}^{A\rightarrow B} \vert^2 }{\varepsilon_i - \varepsilon_n}
  \end{equation*}
  \vskip0.4ex
\end{block}
\end{textblock*}

@@

\begin{textblock*}{367mm}(463mm,233mm)
\begin{exampleblock}{Types of matrix elements of OEP operators}
\vskip0.1ex
\begin{table}[b]
\begin{tabular}{lcccc}
Matrix element      &&            `Overlap-like'                &&            `Coulomb-like'               \\ 
                    && $\tBraKet{i}{\hat{v}_{\rm eff}^{A}}{j} $ && $\tBraKet{j}{\hat{v}_{\rm eff}^{A}}{l}$ \\ 
	\cline{1-5}
Partitioning scheme &&            $i\in A, j\in B$              &&               $j,l\in B$                \\
Associated ERI's    &&            $\BraKet{AA}{AB}$             &&               $\BraKet{AA}{BB}$         \\
Handling            && Density Fitting                          && Distributed Multipoles                  \\
\end{tabular}
%
\end{table}
\vskip-0.1ex
\end{exampleblock}
\end{textblock*}

@@

% - Scheme 
\begin{textblock*}{820mm}(10mm,341mm)
\begin{exampleblock}{Coupling Constant $\boldsymbol{ V_{in}^{A\rightarrow B} } $}
\begin{figure}
\includegraphics[width=1.0\textwidth]{scheme.eps}
\caption{\bf Application of the OEP technique to significantly simplify original theory of Murrell et al.[5] EFP parameters
are shown in blue.}
\end{figure}
\end{exampleblock}
\end{textblock*}

@@

@@

\begin{textblock*}{257mm}(573mm,970mm)
%\begin{exampleblock}{\color{blue} References}
    References: %\\
    \begin{small}
%[1] Gordon, M. S.; Fedorov. D. G.; Pruitt, S. R.; Slipchenko L. V.; \emph{Chem. Rev.} {\bf 2012}, 112, 632
[1] Gordon, M. S. et al.; \emph{Chem. Rev.} {\bf 2012}, 112, 632 
[2] Li, H.; Gordon, M. S.; \emph{J. Chem. Phys.} {\bf 2006}, 124, 214108
[3] Xu, P.; Gordon, M. S.; \emph{J. Chem. Phys.} {\bf 2013}, 139, 194104
[4] Kaliman, I. A.; Slipchenko, L. V.; \emph{J. Comput. Chem.} {\bf 2015}, 36, 129
[5] Murrell, J. N.; Randic, M.; Williams O. R.; \emph{Proc. Roy. Soc. A} {\bf 1965}, 284, 566
    \end{small}         
%\end{exampleblock}
\end{textblock*}
\begin{textblock*}{257mm}(573mm,964mm)
\noindent\rule{83cm}{5.4pt}
\end{textblock*}

@@

%
%
%% ----------------------- SUMMARY
%%
%
% --------------------- ACKNOWLEDGEMENTS
\begin{textblock*}{820mm}(10mm,1070mm)
\begin{block}{Acknowledgements}
 This project is carried out under POLONEZ programme which has received funding from the European Union's
 Horizon~2020 research and innovation programme under the Marie Sk{\l}odowska-Curie grant agreement 
 No.~665778. This project is funded by National Science Centre, Poland 
 (grant~no. 2016/23/P/ST4/01720) within the POLONEZ 3 fellowship.
 We thank
 Wroc{\l}aw Centre for Networking and Supercomputing (WCSS) for
 providing high quality computational resources.
\end{block}
\end{textblock*}

>>>>

% --- Motivation

\begin{textblock*}{440mm}(10mm,135mm)
\begin{block}{Ab Initio Charge Transfer Energy in Fragment-Based Modelling}
 \begin{itemize}
   \item CT energy is an {\color{green} important} stabilizing contribution to the total interaction energy [1]
   \item It is {\color{red} very costly} to compute and generally not directly included in most force fields
   \item {\color{green} EFP2 model} implements efficient CT energy estimator [2,3]
   \item However, EFP2 CT energy is {\color{red} 30-40 times slower} then evaluating other components [3]
   \item In effect, this CT term is usually {\color{red} not included} in condensed matter modelling [4]
 \end{itemize}
 \vskip0.4ex
\end{block}
\end{textblock*}

% --- Our method

\begin{textblock*}{250mm}(10mm,261mm)
\begin{block}{Our Approach}
 \begin{itemize}
   \item Consider Murrell et al.'s perturbation theory [5]
   \item Apply OEP method to eliminate ERI's
   \item Adapt the CT term to the EFP2 method [2,3]
 \end{itemize}
\end{block}
\end{textblock*}

\begin{textblock*}{180mm}(270mm,261mm)
\begin{block}{CT energy by Murrell et al. [5]}
  \vskip-2ex
  \begin{equation*}
    \Delta E_{\rm CT}^{A\rightarrow B} = 2\sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir}
     \frac{\vert V_{in}^{A\rightarrow B} \vert^2 }{\varepsilon_i - \varepsilon_n}
  \end{equation*}
  \vskip0.4ex
\end{block}
\end{textblock*}

@@

\begin{textblock*}{367mm}(463mm,233mm)
\begin{exampleblock}{Types of matrix elements of OEP operators}
\vskip0.1ex
\begin{table}[b]
\def\arraystretch{1.2}
\begin{tabular}{lcccc}
Matrix element      &&            `Overlap-like'                &&            `Coulomb-like'               \\ 
                    && $\tBraKet{i}{\hat{v}_{\rm eff}^{A}}{j} $ && $\tBraKet{j}{\hat{v}_{\rm eff}^{A}}{l}$ \\ 
	\cline{1-5}
Partitioning scheme &&            $i\in A, j\in B$              &&               $j,l\in B$                \\
Associated ERI's    &&            $\BraKet{AA}{AB}$             &&               $\BraKet{AA}{BB}$         \\
Handling            && Density Fitting                          && Distributed Multipoles                  \\
\end{tabular}
%
\end{table}
\vskip-0.1ex
\end{exampleblock}
\end{textblock*}

@@

% - Scheme 
\begin{textblock*}{820mm}(10mm,355mm)
\begin{exampleblock}{Coupling Constant $\boldsymbol{ V_{in}^{A\rightarrow B} } $}
\begin{figure}
\includegraphics[width=1.0\textwidth]{scheme-r1.eps}
\vskip0.9ex
\caption{\bf Application of the OEP technique to significantly simplify original theory of Murrell et al. [5] 
             EFP parameters are shown in blue.}
\end{figure}
\end{exampleblock}
\end{textblock*}

@@

% --- Summary and References

@@

\begin{textblock*}{257mm}(573mm,970mm)
    References: %\\
    \begin{small}
%[1] Gordon, M. S.; Fedorov. D. G.; Pruitt, S. R.; Slipchenko L. V.; \emph{Chem. Rev.} {\bf 2012}, 112, 632
[1] Gordon, M. S. et al.; \emph{Chem. Rev.} {\bf{\small 2012}}, 112, 632 
[2] Li, H.; Gordon, M. S.; \emph{J. Chem. Phys.} {\bf{\small 2006}}, 124, 214108
[3] Xu, P.; Gordon, M. S.; \emph{J. Chem. Phys.} {\bf{\small 2013}}, 139, 194104
[4] Kaliman, I. A.; Slipchenko, L. V.; \emph{J. Comput. Chem.} {\bf{\small 2015}}, 36, 129
[5] Murrell, J. N.; Randic, M.; Williams O. R.; \emph{Proc. Roy. Soc. A} {\bf{\small 1965}}, 284, 566
    \end{small}         
\end{textblock*}
% ----- RULE DIVIDING RESULTS AND REFERENCES
\begin{textblock*}{257mm}(573mm,964mm)
\noindent\rule{83cm}{5.4pt}
\end{textblock*}

@@

% --------------------- ACKNOWLEDGEMENTS
\begin{textblock*}{820mm}(10mm,1070mm)
\begin{block}{Acknowledgements}
 This project is carried out under POLONEZ programme which has received funding from the European Union's
 Horizon~2020 research and innovation programme under the Marie Sk{\l}odowska-Curie grant agreement 
 No.~665778. This project is funded by National Science Centre, Poland 
 (grant~no. 2016/23/P/ST4/01720) within the POLONEZ 3 fellowship.
 We thank
 Wroc{\l}aw Centre for Networking and Supercomputing (WCSS) for
 providing high quality computational resources.
\end{block}
\end{textblock*}
